Relationships in the extremes and their influence on competition and coexistence

### 2022-02-16 paper/Paper.Rnw
some edits to results

Fig.\ref{fig:fig6} displays the subsets of environmental parameters for which coexistence occurs or fails and the degree of ATA contribution to the IGR. Specific to this model and parameter ranges, because $\Delta_i^{[EC]}$ is always positive, all positive values of $\Delta_i^{[EC]}/\text{IGR}$ indicate coexistence and negative values of $\Delta_i^{[EC]}/\text{IGR}$ indicate failure of coexistence. Futhermore, ATA exlusion does not occur and ATA rescue occurs in positive cases where $\Delta_i^{[EC]}>\text{IGR}$. To preserve simplicity and readibility of the plots, $|\Delta_i^{[EC]}/\text{IGR}>1|$ were capped at $|1|$. Higher magnitudes of $\Delta_i^{[EC]}/\text{IGR}$ tended to occur as the IGR became smaller and smaller, thus creating the sharp contrast in the plots where highest intensity positive spaces quickly change into highest intensity negative spaces with decreasing parameters. Like the result of Fig. \ref{fig:fig5}, we see in Fig. \ref{fig:fig6} that amplitude and mean temperature have the most influence on coexistence. Coexistence occurs as $\theta_0$ and $a$ increase and $\Delta_i^{[EC]}/\text{IGR}$ changes from negative to positive. The effect of varying periodicity of environmental fluctuations is...

>>>>

Fig.\ref{fig:fig6} displays the subsets of environmental parameters for which coexistence occurs or fails and the degree of ATA contribution to the IGR. Specific to this model and parameter ranges, because $\Delta_i^{[EC]}$ is always positive, all positive values of $\Delta_i^{[EC]}/\text{IGR}$ indicate coexistence and negative values of $\Delta_i^{[EC]}/\text{IGR}$ indicate failure of coexistence. Futhermore, ATA exlusion does not occur and ATA rescue occurs in positive cases where $\Delta_i^{[EC]}>\text{IGR}$. To preserve simplicity and readibility of the plots, $|\Delta_i^{[EC]}/\text{IGR}>1|$ were capped at $|1|$. Higher magnitudes of $\Delta_i^{[EC]}/\text{IGR}$ tended to occur as the IGR became smaller and smaller, thus creating the sharp contrast in the plots where highest intensity positive spaces quickly change into highest intensity negative spaces with decreasing parameters. Like the result of Fig. \ref{fig:fig5}, we see in Fig. \ref{fig:fig6} that amplitude and mean temperature have the most influence on coexistence and the effect of periodicity of temperature fluctuation is small. Coexistence occurs as $\theta_0$ and $a$ increase and $\Delta_i^{[EC]}/\text{IGR}$ changes from negative to positive.
